Financialisation of Commodity Markets \\\large{Co-movement Behind-the-Scenes}

### 2025-08-25 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@16a22e3a403c14e67bce5a71fdf7b2e77fde2afa 🚀

>>>>

\section*{Figures}\label{figures}
\addcontentsline{toc}{section}{Figures}

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-estimates-1.pdf}

}

\caption{\label{fig-estimates}This figure compares the evolution of
estimates for mean (top panel) and volatility (bottom panel) for
individual commodity returns across three period transitions: past →
financialisation, financialisation → crisis and crisis → post-crisis.
Each stacked bar shows how many cases fall into two categories: yellow
(the estimate in the previous period is smaller than in the next period)
and blue (the estimate in the previous period is larger than in the next
period); numbers inside the bars indicate the count of observations in
each category. Detailed results are available in the attached
\href{https://bautheac.shinyapps.io/co-movement/}{Internet Appendix}.
Period definitions are discussed in Section~\ref{sec-methods} while the
results are discussed in Section~\ref{sec-results}.}

\end{figure}%

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-regimes-1.pdf}

}

\caption{\label{fig-regimes}This figure compares estimates for mean (top
panel) and volatility (bottom panel) for individual commodity returns
between \textbf{CHP} regime phases (\textbf{backwardation}
vs.~\textbf{contango}) for the four periods. Each stacked bar shows how
many cases fall into two categories: yellow (the estimate for the
\textbf{backwardation phase} is smaller than for the \textbf{contango}
phase) and blue (the estimate for the \textbf{backwardation phase} is
greater than for the \textbf{contango} phase); numbers inside the bars
indicate the count of observations in each category.
\textbf{Backwardation} and \textbf{contango} regimes as well as period
definitions are discussed in @sec-methods while the results are
discussed in @sec-results.}

\end{figure}%
